---
title: "Customer Segmentation"
author: "Created by James Rohloff"
output: github_document
params:
    interactive: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    fig.align = "center")
```

```{r}
# Load Required Packages
library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel)
```

```{r}
# Source Scripts
source("scripts/funcs_get_and_plot_customer_info.R")
```

```{r}
# Read CSV File
bike_data_tbl <- read_csv("data_clean/bike_data.csv")
```

## Problem Statement

Marketing would like to increase email campaign engagement by segmenting the customer-base using their buying habbits. 

## Solution Summary

The data science team has identified 4 customer segments. The 4 customer segments were given descriptions based on the customer's top product purchases. 

1. __Segment 1 Preferences:__ Road Bikes, Above $3,200 (Premium Models)

2. __Segment 2 Preferences:__ Road Bikes, Below $3,200 (Economical Models)

3. __Segment 3 Preferences:__ Mountain Bikes, Above $3,200 (Premium Models)

4. __Segment 4 Preferences:__ Both Mountain and Road, Below $3,200 (Economical Models)

## Customer Preferences

### Heat Map

Our customer-base consists of 30 bike shops. Several customers have purchasing preferences for Road or Mountain Bikes based on the proportion of bikes purchased by category_1 and category_2.

```{r Customer Heat Map, fig.height=12}
# Plot Customer Heat Map
plot_customer_heatmap(interactive = params$interactive)
```

### Customer Segmentation

This is a 2D Projection based on customer similarity that exposes 4 clusters, which are key segments in the customer base. 

```{r Customer Segments, fig.height=8}
# Plot Customer Segments
plot_customer_segments(k = 4, seed = 0, interactive = params$interactive)
```

### Customer Preferences By Segment

The 4 customer segments were given descriptions based on the customer's top product purchases. 

1. __Segment 1 Preferences:__ Road Bikes, Above $3,200 (Premium Models)

2. __Segment 2 Preferences:__ Road Bikes, Below $3,200 (Economical Models)

3. __Segment 3 Preferences:__ Mountain Bikes, Above $3,200 (Premium Models)

4. __Segment 4 Preferences:__ Both Mountain and Road, Below $3,200 (Economical Models)

```{r Customer Preferences by Cluster, fig.height=8}
# Plot Customer Preferences by Cluster
plot_customer_preferences_by_cluster(top_n_products = 5, k = 4, seed = 0, interactive = params$interactive)
```
